% Henrique Noronha Facioli
% henrique dot facioli at_ gmail.com

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[british]{babel}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{times}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\setlength{\textwidth}{5.1in} % Text width of the document
\topmargin=-0.3in
\usepackage{roboto}

\usepackage[super]{nth}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Henrique Noronha Facioli} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{+55 11 98397 9278}
\moveleft.5\hoffset\centerline{henrique.facioli@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

\section{EDUCATION}

{\bf Bachelor in Computer Engineering} \hfill Feb 2014 - Dec 2018 \\
State University of Campinas, UNICAMP, Brazil.

\section{SKILLS}
{\sl Strong:} Python, C++, C \\
{\sl Knowledgeable:} Git, Java, JavaScript, Linux Device Drivers, Lisp, SQL, Shell Script

{\sl Spoken language:} Portuguese (mother tongue) and English (fluent)

\section{ACADEMIC}

{\bf Undergraduate Research} \hfill Mar 2015 - Present \\
Project Stream - Development of a code profiler for ARM architecture funded by a Samsung Scholarship \
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Assisted the design and development of a dynamic profiler to catch hotspots on code for ARM architecture.
\end{itemize}
{\bf Teaching Assistant} \hfill Feb 2016 - Jul 2016 \\
Algorithm and Computer Programming at Unicamp, Brazil \
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Assisted and guided students on practical exercises using C programming language.
\end{itemize}


\section{EXTRA-CURRICULAR}
{\bf Personal Projects}
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Unicamp Computing Students Union Administration System and Website\\
	 - Redesigned the system and led the implementation of the website and management software. Used Python and JavaScript.
\item Unicamp Computing Academic Week Administration System\\
	 - Implemented login management, event scheduler and an e-commerce using \\ JavaScript [Node.js].
\item Unicamp courses evaluation system (GD-AE-)\\
	 - Designed and implemented a software to help students choose Unicamp courses and programs based on others student's experiences. Used Python and JavaScript.
\end{itemize}

{\bf Administrative Officer} \hfill Oct 2014 - Oct 2016 \\
CACo (Centro Acadêmico da Computação) - Unicamp Computing Students Union
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Worked on events organization, legal administration and resources management.
\end{itemize}

{\bf Financial Administrative Officer} \hfill Jan 2015 - Dec 2015 \\
SECOMP (Semana Acadêmica da Computação) - Unicamp Computing Academic Week
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Worked in estimating costs and contacting sponsors.
\end{itemize}

{\bf Undergraduate Representative} \hfill Jun 2015 - Jun 2017 \\
Institute of Computing and on Faculty of Electrical and Computer Engineering Institute \\ Affairs Commission at Unicamp, Brazil.
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Represented students interests on Affairs Commission.
\end{itemize}

\end{resume}
\end{document}
