% Henrique Noronha Facioli
% henrique dot facioli at_ gmail.com
% curriculum to 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage[british]{babel}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{times}
\usepackage{textcomp}
\usepackage[T1]{fontenc}
\usepackage{helvet} 
\setlength{\textwidth}{5.1in} % Text width of the document
\topmargin=-0.3in
\usepackage{roboto}

\usepackage[super]{nth}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Henrique Noronha Facioli} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
% \moveleft.5\hoffset\centerline{1163 West Peachtree St Ne Unit 2603} % Your address
% \moveleft.5\hoffset\centerline{Atlanta, Georgia 30309}
\moveleft.5\hoffset\centerline{+55 11 983-979-278}
\moveleft.5\hoffset\centerline{henrique.facioli@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

\section{EDUCATION} 

{\bf Bachelor in Computer Engineering} \hfill Feb 2014 - Expected Dec 2018 \\
State University of Campinas, Unicamp, Brazil.
 
\section{ACADEMIC}

{\bf Undergraduate Research} \hfill Mar 2015 - Present \\
Project Stream - Computer System Laboratory (LSC) - Unicamp/Samsung \
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Assisted the design and development of a dynamic profiler to find hotspots on code for ARM architecture.
\end{itemize} 
{\bf Teaching Assistant} \hfill Feb 2016 - Jul 2016 \\
Algorithms and Computer Programming at Unicamp, Brazil \
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Assisted and oriented students on exercises and practical laboratory using C programming language.
\end{itemize}

\section{VOLUNTEER}

{\bf Personal Projects}
\begin{itemize} \itemsep -1pt % Reduce space between items
\item \href{https://github.com/cacounicamp/Site}{Unicamp Computing Students Union Website and Administration System} \\
	 - Redesigned the system and lead the implementation of the website and management software. Used Python and JavaScript.
\item \href{https://github.com/henriquefacioli/secomp-painel}{Unicamp Computing Academic Week Administration System}\\
	 - Implemented login management, event scheduler and an e-commerce using JavaScript [Node.js].
\item \href{https://github.com/henriquefacioli/gd-ae-}{Unicamp teaching evaluation software}\\
	 - Designed and implemented a software to help students choose disciplines based on others student's experiences. Used Python and JavaScript.
\end{itemize}

{\bf Administrative Officer} \hfill Oct 2014 - Oct 2016 \\
CACo (Centro Acadêmico da Computação) - Unicamp Computing Students Union 
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Acted on events organization, legal administration and resources management.
\end{itemize}

{\bf Financial Administrative Officer} \hfill Jan 2015 - Dec 2015 \\
SECOMP (Semana Acadêmica da Computação) - Unicamp Computing Academic Week 
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Estimated costs and contacted possible donators to raise money.
\end{itemize}

{\bf Undergraduate Representative} \hfill Jun 2015 - Jun 2017 \\
Institute of Computing and on Faculty of Electrical and Computer Engineering Institute \\ Affairs Commission at Unicamp, Brazil. 
\begin{itemize} \itemsep -1pt % Reduce space between items
\item Represented students interests on Affairs Commission.
\end{itemize}

\section{SKILLS} 
{\sl Strong:} Python, C++, C \\
{\sl Knowledgeable:} Git, Java, JavaScript, Linux Device Drivers, Lisp, SQL, Shell Script

\section{LANGUAGES}
{\sl English:} Fluent \\
{\sl Portugues:} Native \\
{\sl Spanish:} Basic \\
{\sl Mandarin:} Basic \\

\end{resume}
\end{document}